Tabular Constraint Learning

### 2016-04-13 Paper/ECAI/tabular.tex
fixed typo

A \textit{tabular solution} $S$ to an spreadsheet constraint $C$ is a tuple $(X_1, \dots, X_n)$ where $n$ is the number of variables in $C$ and each $X_i$ is a subgroup in \groups, such that $(X_1,\dots,X_n)$ satisfies both the \CSignature and \CFunction of the constraint $C$.

@@

\begin{minipage}[c]{14em}
  \vspace{5pt}
  \begin{tabular}{ll}
    \multicolumn{2}{l}{{\textbf{Tabular Constraint Learning Problem}}}\\
    \vspace{-4pt}
    &\\
    \textbf{Given:}& the set of all groups $\groups$ and of spreadsheet constraints $\constraints$\\
    \textbf{Find:}&  all tabular solution $S$ in \groups for each constraint $c$ \constraints \\ 
  \end{tabular}
  \vspace{6pt}
\end{minipage}

>>>>

A \textit{tabular solution} $S$ to a spreadsheet constraint $C$ is a tuple $(X_1, \dots, X_n)$ where $n$ is the number of variables in $C$ and each $X_i$ is a subgroup in \groups, such that $(X_1,\dots,X_n)$ satisfies both the \CSignature and \CFunction of the constraint $C$.

@@

\begin{minipage}[c]{14em}
  \vspace{5pt}
  \begin{tabular}{ll}
    \multicolumn{2}{l}{{\textbf{Tabular Constraint Learning Problem}}}\\
    \vspace{-4pt}
    &\\
    \textbf{Given:}& the set of all groups $\groups$ and of spreadsheet constraints $\constraints$\\
    \textbf{Find:}&  all tabular solution $S$ in \groups for each constraint $c$ in \constraints \\ 
  \end{tabular}
  \vspace{6pt}
\end{minipage}
